---
title: "simpleRegress"
author: "Hayden Wood"
date: "Spring 2024"
output: html_document

---

## Compare all models   

predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```



## Model LENGTH ~ NECK  this is an example  

```{r}
simpNECK <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simpNECK)
```

```{r}
summary.lm(simpNECK)
```

```{r}
simpAGE <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simpAGE)
```

```{r}
summary.lm(simpAGE)
```

```{r}
simpHEADLEN <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simpHEADLEN)
```
```{r}
summary.lm(simpHEADLEN)
```
```{r}
simpHEADWTH <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simpHEADWTH)
```
```{r}
summary.lm(simpHEADWTH)
```


```{r}
simpCHEST <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpCHEST)
```

```{r}
summary.lm(simpCHEST)
```

```{r}
simpWEIGHT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpWEIGHT)
```

```{r}
summary.lm(simpWEIGHT)
```

Best to worst based on adjusted-rsquared
HHEADLEN 0.8434
CHEST 0.7869
NECK 0.7476
WEIGHT 0.7423
HEADWTH 0.5321
AGE 0.5073

## Compare all models that predict LENGTH other than NECCK. THEN order them from worst to best by its value of Adjusted-Rsquared, or by RSE where smaller is better

based on the adjusted Rsquared, this would ditermine that HEADLEN is the best variable ot predict LENGTH.
